Discussion

### 2023-03-10 06_Paper/ER-ED/ERED_Stage2/Discussion.Rmd
added limitation

Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
One might argue that 2 € as an incentive to repeat an entire block is quite low.
However, we chose this amount because, first, we have followed the original paradigm of Westbrook[@Westbrook2013].
Further it was shown that

>>>>

Fourth, the highest value during the discounting paradigm was set to 2 € as fixed value.
Participants should imagine that this was the amount of money they would get when they would repeat this strategy.
Thus, 2 € as an incentive to repeat an entire regulation block could be quite low.
However, we chose this amount because, first, we have followed the original paradigm of Westbrook[@Westbrook2013].
Further it was shown that at least in cognitive effort discounting, a lower incentive could even increase sensitivity in participants for differences in effort[@Bialaszek2017].
n the future, however, it should be examined how the level of incentives affects subjective values.
